I would like to thank my supervisors Dr Adam Cribbs, Professor Udo Oppermann and Dr Sarah Gooding for all of their support and guidance throughout my DPhil.
Adam for teaching me about computational biology and inspiring me to pursue it as a career, Sarah for being a wealth of knowledge in multiple myeloma, and Udo for being a great group leader and offering me incredible opportunities.

I would also like to thank Dr James Dunford and Graham Wells for all of their knowledge in the wet lab, and generously giving up so much of their time to help me with my experiments (and only teasing me slightly for my \textit{many} lab blunders).
I am grateful and thankful to Dr Martin Philpott for his expertise in everything sequencing.
I would also like to thank past lab members who greatly enriched my DPhil experience, Dr Filiz Senbabaoglu, Dr Chao Mike Jiang and Dr Henry Lee.

I'd like to thank Professor Afsie Sabokbar for all of her kindness and support during my time at NDORMS. 
I'm thankful to SABS directors, Professor Garrett Morris and Professor Charlotte Deane, for the fantastic opportunity to pursue a DPhil at the University of Oxford. 
I am also grateful for SABS and the DTC for teaching me how to code, and for introducing me to my fabulous SABS cohort. 

I'd like to thank my partner, Evan Roberts, for helping me with all my computer related problems (from cellular automata, to environment issues, to taking it upon himself to speed my code up by 1 millisecond), and for procrastinating away from his own DPhil to do so. 
I am also tremendously grateful to SHCBC and its members for keeping me sane over the last four years, in particular, Beth Bryan and Julia Halligan.
I'd like to thank my UCL pals, school friends and Karate family for being there for me, and giving me the chance to vent about my DPhil, even when it gets incredibly tedious. 

Most of all, I'd like to thank my family and dedicate this thesis to them.
Pamela James, for being the most supportive and caring mum in the world, and proof reading everything I've ever written, despite having no idea what most of it means.
My dad, Michael Bott, for coming to all my football games (even at the age of 25) and being my biggest fan.
And my sister and best friend, Alexandra James-Bott, who has the unique ability to cheer me up and make me laugh no matter the situation.
I'm also grateful to the rest of my family, Daniel, Nancy, Spike, Auntie Lorraine and Gary.

The work in this thesis has been kindly supported by the Engineering and Physical Sciences Research Council (EPSRC) and GSK.